TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-07 paper/paper.tex
updates to paper

@@

% Copied from proposal
% Edited 27-11-2017

Multitentant datacenters aim to provide services with consistent performance
and reliability. When customers send a lot of data in a short amount of time,
networks might become congested, which results in lowered performance.

Congestion occurs when a buffer on the path to the recipient is full and
packets are dropped. TCP has a mechanism to avoid congestion in the network:
TCP congestion control. Multiple algorithms are available for congestion
control and show a different behaviour depending on the network's
characteristics.

In 2010, the algorithm DCTCP was described in an
article\cite{dctcp-congestion-original} and published as RFC8257 in
2017\cite{dctcp-congestion}. DCTCP is optimized for datacenters and provides a
high-burst tolerance, low latency, and high throughput when the datacenter has
a small part of the buffer available\cite{dctcp-congestion}. In 2016 another
algorithm was proposed: BBR. This is a TCP congestion algorithm created by
Google, which achieves higher bandwidths and lower latencies compared to other
TCP congestion methods\cite{bbr-congestion}. A comparison of BBR with
CUBIC\cite{bbr-congestion-comparison} shows that the BBR node pushes the CUBIC
node away in bandwidth when using small buffers. The BBR node gets more
bandwidth allocated than the CUBIC node.

@@

@@

	In scenario 1 the TCP congestion algorithm is tested for fairness in sharing bandwidth with other TCP connections using other TCP congestion algorithms. In order to test the fairness of bandwidth shares, the bandwidth allocation per algorithm is measured. It can be determined whether a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more or less bandwidth to that specific TCP connection.

@@

		\subsubsection{Algorithm Characteristics}

		- Includes characteristics of the algorithms. To what do the TCP congestion algorithms respond according to literature? And how do they deal with that (If available in literature).

>>>>

TCP congestion control algorithms aim to divide the available bandwidth fairly
among network users. In datacenters, many tenants share a limited amount of bandwidth.
If too many tenants TODO luc

@@

Multitentant datacenters aim to provide services with consistent performance
and reliability. When customers send a lot of data in a short amount of time,
networks might become saturated or even congested, and bandwidth needs to be
distributed fairly among tenants.

Congestion occurs when a buffer on the path to the recipient is full and
packets have to be dropped. TCP uses a congestion control algorithm to avoid
congestion in the network and distribute bandwidth fairly among users. Several
algorithms are available to perform this function. Each has a different behaviour
depending on the network's characteristics.

@@

% todo make this logical
In 2010, the algorithm DCTCP was described in an
article\cite{dctcp-congestion-original} and published as RFC8257 in
2017\cite{dctcp-congestion}. DCTCP is optimized for datacenters and provides a
high-burst tolerance, low latency, and high throughput when the datacenter has
a small part of the buffer available\cite{dctcp-congestion}. In 2016 another
algorithm was proposed: BBR. This is a TCP congestion algorithm created by
Google, which achieves higher bandwidths and lower latencies compared to other
TCP congestion methods\cite{bbr-congestion}. A comparison of BBR with
CUBIC\cite{bbr-congestion-comparison} shows that the BBR node pushes the CUBIC
node away in bandwidth when using small buffers. The BBR node gets more
bandwidth allocated than the CUBIC node.

@@

	In scenario 1 the TCP congestion algorithm is tested for fairness in sharing bandwidth with other TCP connections using other TCP congestion algorithms. In order to test the fairness of congestion algorithms, the bandwidth allocation per algorithm is measured. It can be determined whether a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more or less bandwidth to that specific TCP connection.

@@

		\subsubsection{Algorithm Characteristics}
		The BBR algorithm depends on the parameters BBR.BtlBw and BBR.RTprop. Those parameters are estimates defined by the BBR algorithm. \\texttt{BtlBw} contains the bandwidth available to data transmissions ...
		- Includes characteristics of the algorithms. To what do the TCP congestion algorithms respond according to literature? And how do they deal with that (If available in literature).
